\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{calc,trees,positioning,arrows,chains,shapes.geometric,%
    decorations.pathreplacing,decorations.pathmorphing,shapes,%
    matrix,shapes.symbols}

\begin{document}

Since the defocused images of seed particles are fuzzy rings, the task of
tracking the micron-scale particles is to identify the rings of various sizes
on each frame and reconstruct their trajectories. For this project, We have
developed a fast algorithm based on Hough Transform for particle tracking.
With the help of UFO framework, we implement our new algorithm easily on
graphic cards. Compared to old software using order statistic filter algorithm,
the performance of our new algorithm is boosted by a factor 500.

The flow of our algorithm is shown in Fig. \ref{fig:alguptv}.  Standard image
processing filters, like local contrast enhancement and noise reduction, are
first applied to the input images, then they are sent to Hough Transform
filter. In our problem, standard procedure of edge detection before HT does not
apply, since the rings are fuzzy and do not have crisp edges. To overcome this
problem, we have devised an efficient blob detection algorithm, because the HT
votes at the ring center tend to have the shape of blurred blob.  Our method is
very effective in finding the ring candidates. In order to eliminate the false
positives in the candidates, we further use a azimuthal filter, which is a test
on the pixel histogram in radius direction respect to the center of candidate
ring. Another benifit from using the azimuthal filter is,  that the position of
the the ring center can be determined to pixel level by fitting histogram around
the peak position against a gaussian function.


The UFO framework let us develop software in OpenCL with relative ease and
distribute the more computational intensive part on to graphic cards. We have
developed GPU kernel programs for all filters apart from the azimuthal test,
which is more suitable for execution on CPU cores. Benchmarking on our particle
tracking software shows that it takes roughly 400ms to process each frame on a
computer with Nvidia GTX Titan GPU cards and Xeon E3-1200 CPU.  

\input{uptv.tex}

\begin{table}[t]
\centering
\begin{tabular}{c c}
\hline
\textbf{Algorithm} & \textbf{Benchmark} \\
\hline
Order Statistic Filter & 200~s \\
Hough Transform & 400~ms \\
\hline
\end{tabular}
\caption{Benchmark: Hough transform compared to order statistic filter algorithm.}
\end{table}


\end{document}
